Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-10 main.tex
graphs

\usepackage{tikz}
\usepackage{amsthm}\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]

@@

\newcommand{\fequ}{\equiv}
\newcommand{\fequp}{\mathrel{\equiv'\mkern-2mu}}

\newcommand{\graph}[1]{\mathcal{#1}}
\newcommand{\vertices}[1][]{\ifthenelse{\isempty{#1}}{V}{V_{\graph{#1}}}}
\newcommand{\edges}[1][]{\ifthenelse{\isempty{#1}}{E}{E_{\graph{#1}}}}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\newcommand{\compl}[1]{#1^\complement}
\newcommand{\sublist}[1]{\set{#1}}
\newcommand{\subst}[2]{#1\mathord{\scriptstyle\mapsto} #2}
\newcommand{\ssubst}[2]{\sublist{\subst{#1}{#2}}}

@@

In this paper we use the sequent calculus $\FOLK$, shown in
Figure~\ref{fig:LK1}, which is a one-sided variant of Gentzen's
original calculus~\cite{gentzen:35:I} for first-order logic. To
simplify some technicalities later in this paper, we also include here
the $\mixr$-rule. The linear fragment of $\FOLK$, i.e., the fragment
without the rules $\conr$ (\emph{contraction}) and $\weakr$
(\emph{weakening}) defines \emph{first-order multiplicative linear
logic}~\cite{girard:87,girard:88} \emph{with
mix}~\cite{fleury:retore:94,bellin:97}~(MLL1+mix). We denote that system
here with $\FOMLL$ (shown in Figure~\ref{fig:LK1} in the dashed box).

@@

A graph $\gG$ is \bfit{labelled} in a set $L$ if
each vertex $v\in\vG$ has an element $\ell(v)\in L$ associated with it, its \bfit{label}.

@@

An
\bfit{undirected graph} $G = (V, E)$ consists of a finite set $V$ of vertices
and a set of $E$ of \bfit{undirected edges} (two-element subsets of $V$).
For a given (directed or undirected) graph $G$, we write $V_G$ and $E_G$ for its
vertex and edge sets respectively. We write $vw$ for an edge $(v, w)$ or $\{v,
w\}$. Let $G = (V, E)$ and $G' = (V', E')$ be two undirected graphs. Without
loss of generality, we assume that $V$ and $V'$ are disjoint. The \bfit{union}
$G + G'$ is the graph $(V \cup V', E \cup E')$ and the \bfit{join} $G \times G'$
is the graph $(V \cup V', E \cup E' \cup \{vv' | v \in V, v' \in V'\})$. A
\bfit{cograph} is a $P_4$-free undireced grpah, i.e., for any distinct vertices $v_1,
v_2, v_3, v_4 \in V$, the restriction of the edge sets on them is not equal to
$\{v_1v_2, v_2v_3, v_3v_4\}$. In a graph $G = (V, E)$, the \bfit{neighbourhood}
$N(v)$ of $v \in V$ is defined as the set $\{w | vw \in E\}$, a set $W \subseteq
V$ induces a \bfit{matching} if for all $w \in W$, $N(w) \cap E$ is a singleton, and a module is a
set $M \subseteq V$ such that $N(v) \ M = N(w) \ M$ for all $v, w \in M$. A
\bfit{module} $M$ is strong if for every module $M'$, we have $M' \subseteq M$, $M
\subseteq$ or $M \cap M' = \emptyset$. A \bfit{graph homomorphism} $f: (V, E)
\rightarrow (V', E')$ is a function $f : V \rightarrow V'$ such that $f(v)f(w)
\in E'$ whenever $vw \in E$.
\subsection{Fographs}

A cograph is \bfit{logical} if every vertex is labelled either by an atom or variable,
and it has at least one atom-labelled vertex. We denote by $label_G(v)$, or simply
$label(v)$ the label of a vertex in a logical cograph $G$. An atom-labelled vertex is called
a \bfit{literal} and a variable-labelled vertex is called a \bfit{binder}. A
binder labelled with $x$ is called an \bfit{$x$-binder}. The \bfit{scope} of a binder
$b$ is the smallest strong module containing at least two vertices, including
the binder itself. An \bfit{$x$-literal} is a literal whose atom contains the variable $x$. An $x$-binder \bfit{binds} every $x$-literal in its scope.
In a logical cograph $G$, a binder $b$ is \bfit{existential} (resp. \bfit{universal}) if, for every other
vertex $v$ in its scope, we have $bv \in E_G$ (resp. $bv \notin E_G$). An
$x$-binder is \bfit{legal} if its scope contains no other $x$-binder and at least one
literal.

We now introduce first-order graphs which are used to represent first-order formulas.

\begin{definition}
A \bfit{first-order graph} or \bfit{fograph} is a logical cograph with legal binders.
\end{definition}

For a formula $A$, we can define its associated fograph $\Gr(A)$ inductively by: $\Gr(\alpha) = \cdot \alpha$ (a single-vertex graph whose vertex is labelled by $\alpha$); $\Gr(A \cor B) = \Gr(A) + \Gr(B)$ and $\Gr(A \cand B) = \Gr(A) \times \Gr(B)$.
The \bfit{binding graph} of a forgraph $G$ is the directed graph $(V_G, \{(b,
l) \ | \ b \text{ binds } l\})$.

@@

In a fograph, two atoms are \bfit{pre-dual} if their predicate symbols are dual
(e.g. $pxy$ and $\overline{p}yz$) and two literals are \bfit{pre-dual} if their
labels (atoms) are pre-dual. A \bfit{linked fograph} is a coloured fograph such
that every colour, called a \bfit{link}, consists of two pre-dual literals, and
every literal is either $\ttt$-labelled or in a link.

@@

@@

\begin{definition}
A \bfit{first-order combinatorial proof} of a fograph $G$ is a skew
bifibration $f: N \rightarrow G$ where $N$ is a fonet. A \bfit{first-order
combinatorial proof} of a formula $A$ is a combinatorial proof of its graph
$\Gr(A)$.
\end{definition}

@@

\begin{proposition}
\label{prop2}
Let $u$ and $v$ be two distinct vertices of a fograph $\Gr(A)$, then we have the equivalence
between:
\begin{itemize}
  \item $u$ and $v$ are adjacent in $\Gr(A)$
  \item $u$ and $v$ are connected by a switching path of $\FT(A)$, and if one of them is a universal quantifier, then the other is
	not a descendant of the former.
  \end{itemize}
\begin{proof}
By induction on $A$.
\begin{itemize}
  \item If $A$ is an atom, trivial.
  \item If $A = A_1 \cand A_2$, then we distinguish two cases:
    \begin{itemize}
      \item $u$ and $v$ are both in $A_1$ (resp. $A_2$): trivial by
	      the induction hypothesis.
      \item one of them is in $A_1$ and the other is in $A_2$: they are
	      adjacent in $\Gr(A)$ by definition. By Proposition \ref{prop1},
		    the one in $A_1$ (resp. $A_2$) is connected to the
		    vertex representing $A_1$ (resp. $A_2$) by a switching
		    path. Together with the two edges incident to $A_1 \cand
		    A_2$, we obtain a switching path connecting $u$ and $v$.
    \end{itemize}
  \item If $A = A_1 \cor A_2$, then we distinguish two cases:
    \begin{itemize}
      \item $u$ and $v$ are both in $A_1$ (resp. $A_2$): trivial by
	      the induction hypothesis.
      \item one of them is in $A_1$ and the other is in $A_2$: they are not
	      adjacent in $\Gr(A)$ by definition. It is clear that they
		    are not connected by a switching path.
    \end{itemize}
  \item If $A = \exists x \ A'$, then we distinguish two cases:
    \begin{itemize}
      \item $u$ and $v$ are both in $A'$: trivial by the induction
	      hypothesis.
      \item one of them is $\exists x$ and the other is in $A'$: trivial
	      by Proposition \ref{prop1}

    \end{itemize}
  \item If $A = \forall x \ A'$, then we distinguish two cases:
    \begin{itemize}
      \item $u$ and $v$ are both in $A'$: trivial by the induction
	      hypothesis.
      \item one of them is $\forall x$ and the other is in $A'$:
	      they are not adjacent in $\Gr(A)$ by definition and it is clear that
		    the former is a descendant of $\forall x$.
    \end{itemize}
\end{itemize}
\end{proof}
\end{proposition}

\begin{proposition}
If there exists an induced bimatching of the linked fograph $G = \Gr(A)$, then there exists a switching graph of the corresponding unification net which contains a cycle.
\begin{proof}
  Suppose that there exists a set $W$ inducing a bimatching in $G$.
  Then $(W, E_G)$ and $(W, L_G)$ are matchings.\\
  Let $E_W$ (resp. $L_W$) be the restriction of $E_G$ (resp. $L_G$) to $W$. \\
  If $E_W \cap L_W \neq \emptyset$, then there exist $u$ and $v$ such that $uv
  \in E_G$ and $uv \in L_G$. By Proposition \ref{prop2}, there exists a
  switching path of the formula tree of $A$. Together with the leap
  $uv$, this path induces a cycle in a switching graph of the
  corresponding unification structure. \\
  We can now suppose that $E_W$ and $L_W$ are disjoint. It is not difficult to
  see the existence of an alternating and elementary cycle in the bicoloured graph $(W, E_W \uplus L_W)$, i.e. a cycle of which the edges are alternately in $E_W$ and $L_W$ and containing no two equal vertices.
  By Proposition \ref{prop2}, this cycle induces a cycle in the unification
  structure. Now we want to construct a switching graph that contains this cycle.\\
  Consider a universal quantifier $\forall x$. If $\forall x \notin W$, then        
  we keep the incoming edge from its direct subformula and remove all the 
  dependencies. Otherwise, since $(W, L_G)$ is a matching, there exists a
  unique existential quantifier adjacent to $\forall x$ and we keep thus the
  corresponding edge in the unification structure. \\
  Now consider a $\cor$. We distinguish three cases:
  \begin{itemize}
    \item the cycle goes through none of the two branches (incoming edges) of
	    the $\cor$: we can choose an
	    arbitrary switching for this $\cor$
    \item the cycle goes through exactly one branch: we choose the corresponding
	    switching
    \item the cycle goes through both branches:
	    this means that there exist $v_L \in W$ (resp. $v_R$) in the left
		  (resp. right) branch, $u_L$, $u_R \in W$, such that
		  $u_Lv_L, u_Rv_R \in E_W$ and that the corresponding switching
		  path from $u_L$ to $v_L$ (resp. from $u_R$ to $v_R$) goes
		  through the left (resp. right) edge of $\cor$.

@@

\begin{proposition}
For any context $S$ and any formula $A$:
\begin{itemize}
  \item $\PE{A}$ is a formula containing no quantifier for any formula $A$.
  \item $\Gr(\PE{A}) = \Gr(A)$ by confounding the atoms $U_x$, $E_x$ with the variable
	  $x$. Thus, a map $f : \Gr(\PE{A}) \rightarrow \Gr(\PE{B})$ can be seen as a map
		$f : \Gr(A) \rightarrow \Gr(B)$.
  \item $\PE{(S\{A\})} = \PE{S}\{\PE{A}\}$.
\end{itemize}

@@

Now we prove that each map $g \in \{wk, ac, m, m_1, m_2 \}$ is a skew bifibration. To do that, it suffices to prove that $g$ is a fibration between the corresponding binding graphs since it is already a skew fibration on the corresponding fographs and it is label-preserving and existential-preserving.
\begin{center}
for each $x$-binder $b$ in $\Gr(\PE{B})$, for each vertex $v \in V(\Gr(\PE{A}))$
such that $g(v)$ is bound by $b$, there exists a unique binder $b'$ such
that $b'$ binds $v$.
\end{center}

@@

  Therefore, all of these maps are skew bifibrations and since skew bifibrations
on fographs compose (Lemma 10.32, \cite{hughes:fopws}), there exists a skew
bifibration from $\Gr(A)$ to $\Gr(B)$.

@@

\begin{proof}
By Theorem \ref{thm1}, there exists a formula $A'$ such that there is a proof
$\Pi$ of $A'$ in $\FOMLL$ and a derivation $D$ from $A'$ to $A$ consisting of
the $\wD$ and $\cD$ rules only. The proof $\Pi$ corresponds to a unique
unification net which is equivalent to the fonet corresponding to $\Pi$, i.e.,
the fograph $\Gr(A')$ together with the links of $\Pi$. By Lemma \ref{mlem}, 
there exists a skew bifibration $\Gr(A') \rightarrow \Gr(A)$. We have thus a
combinatorial proof of $A$.

@@

\begin{proof}
Consider the dervation $\Delta''$. If some $U_x$ (or $E_x$) is introduced
via weakening, then all the atoms it binds in $\PE{B}$ should also be introduced 
via weakening. In fact, an atom of $\PE{B}$ is introduced via weakening is 
equivalent to the fact that its corresponding vertex is not in the image of $f$. 
Since there is an edge from $U_x$ (resp. $E_x$) to all the literals it binds in the 
binding graph $\overrightarrow{\Gr(B)}$, if one of the atoms is in the image, 
$U_x$ (resp. $E_x$) should also be in the image since $f$ is a fibration on binding graphs.

>>>>

\usepackage{tikz}
\usepackage{amsthm}\theoremstyle{plain}
\newtheorem{thm}{Theorem}%[section]

@@

\newcommand{\samecol}{\sim}
\newcommand{\fequ}{\equiv}
\newcommand{\fequp}{\mathrel{\equiv'\mkern-2mu}}

\newcommand{\graph}[1]{\mathcal{#1}}
\newcommand{\vertices}[1][]{\ifthenelse{\isempty{#1}}{V}{V_{\graph{#1}}}}
\newcommand{\edges}[1][]{\ifthenelse{\isempty{#1}}{E}{E_{\graph{#1}}}}
\newcommand{\bgraph}[1]{\mathcal{\vec{#1}}}

@@

\newcommand{\bA}{\bgraph{A}}
\newcommand{\bC}{\bgraph{C}}
\newcommand{\bG}{\bgraph{G}}
\newcommand{\bH}{\bgraph{H}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Pfour}{\mathbf{P_4}}

@@

\newcommand{\single}[1]{\bullet#1}

\newcommand{\graphof}[1]{\llbracket#1\rrbracket}
\newcommand{\compl}[1]{#1^\complement}
\newcommand{\sublist}[1]{\set{#1}}
\newcommand{\subst}[2]{#1\mathord{\scriptstyle\mapsto} #2}
\newcommand{\ssubst}[2]{\sublist{\subst{#1}{#2}}}

@@

In this paper we use the sequent calculus $\FOLK$, shown in
Figure~\ref{fig:LK1}, which is a one-sided variant of Gentzen's
original calculus~\cite{gentzen:35:I} for first-order logic. To
simplify some technicalities later in this paper, we also include here
the $\mixr$-rule.

\begin{thm}
  A formula $A$ is a theorem of first-order logic iff the sequent $\sqn A$ is derivable in $\FOLK$.
\end{thm}

The linear fragment of $\FOLK$, i.e., the fragment
without the rules $\conr$ (\emph{contraction}) and $\weakr$
(\emph{weakening}) defines \emph{first-order multiplicative linear
logic}~\cite{girard:87,girard:88} \emph{with
mix}~\cite{fleury:retore:94,bellin:97}~(MLL1+mix). We denote that system
here with $\FOMLL$ (shown in Figure~\ref{fig:LK1} in the dashed box).

@@

A graph $\gG$ is \bfit{labelled} in a set $L$ if each vertex $v\in\vG$
has an element $\ell(v)\in L$ associated with it, its \bfit{label}.  A
graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
equivalence relation $\samcol$ on $\vG$; each equivalence class is a
\bfit{colour}.  A \bfit{vertex renaming} of $\gG=\tuple{\vG,\eG}$
along a bijection $(\hat\cdot)\colon\vG\to\hat\vG$ is the graph
$\hat\gG=\tuple{\hat\vG,\set{\hat v\hat w\mid vw\in\eG}}$, with
colouring and/or labelling inherited (i.e., $\hat v\samcol\hat w$ if
$v\samecol w$, and $\ell(\hat v)=\ell(v)$). Following standard graph
theory, we identify graphs modulo vertex renaming.

@@

A graph $\gH=\tuple{\vH,\eH}$ is a \bfit{subgraph} of a graph
$\gG=\tuple{\vG,\eG}$ if $\vH\subseteq\vG$ and $\eH\subseteq\eG$. It
is \bfit{induced} if $v,w\in\vH$ and $vw\in\eG$ implies $vw\in\eH$.  A
graph is \bfit{$\gH$-free} if it does not contain $\gH$ as an induced
subgraph.  The graph $\Pfour$ is the (undirected) graph
$\tuple{\set{v_1, v_2, v_3, v_4},\set{v_1v_2, v_2v_3, v_3v_4}}$.  A
\bfit{cograph} is a $P_4$-free undirected graph. The interest in
cographs for our paper comes from the following well-known fact.

\begin{thm}[\cite{}]\label{thm:cograph}
  A graph is a cograph iff it can be constructed from the singletons via the operations $+$ and~$\times$.
\end{thm}
\todo{ad the reference}

In a graph $\gG$, the \bfit{neighbourhood} $N(v)$ of a vertex $v \in\vG$ is defined as
the set $\set{w | vw \in\eG}$. 
A \bfit{module} is a set $M \subseteq \vG$ such that $N(v) \ M = N(w) \ M$
for all $v, w \in M$. A module $M$ is \bfit{strong} if for every
module $M'$, we have $M' \subseteq M$, $M \subseteq$ or $M \cap M' =
\emptyset$. A module is \bfit{proper} if it has two or more vertices.

Modules in cographs correspond precisely to the subtrees of the
cotrees (the term-trees constructing the graph via $+$ and~$\times$).

\subsection{Fographs}

A cograph is \bfit{logical} if every vertex is labelled either by an
atom or variable, and it has at least one atom-labelled vertex. We
write $\single\alpha$ for an $\alpha$-labelled vertex. An
atom-labelled vertex is called a \bfit{literal} and a
variable-labelled vertex is called a \bfit{binder}. A binder labelled
with $x$ is called an \bfit{$x$-binder}. The \bfit{scope} of a binder
$b$ is the smallest proper strong module containing $b$.
An \bfit{$x$-literal} is a literal whose
atom contains the variable $x$. An $x$-binder \bfit{binds} every
$x$-literal in its scope.  In a logical cograph $G$, a binder $b$ is
\bfit{existential} (resp. \bfit{universal}) if, for every other vertex
$v$ in its scope, we have $bv \in E_G$ (resp. $bv \notin E_G$). An
$x$-binder is \bfit{legal} if its scope contains no other $x$-binder
and at least one literal.

\begin{definition}
A \bfit{first-order graph} or \bfit{fograph} is a logical cograph with legal binders. The
\bfit{binding graph} of a fograph $\gG$ is the directed graph $\bG=\tuple{\vG,
\set{(b, l) \mid b \text{ binds } l}}$.
\end{definition}

We now define a mapping $\graphof\cdot$ from formulas to (labelled)
graphs, inductively as follows:

For a formula $A$, we can define its
associated fograph $\graphof(A)$ inductively by: $\graphof(\alpha) =
\cdot \alpha$ (a single-vertex graph whose vertex is labelled by
$\alpha$); $\graphof(A \cor B) = \graphof(A) + \graphof(B)$ and
$\graphof(A \cand B) = \graphof(A) \times \graphof(B)$.
\todo{make look nice, use array}

\begin{lemma}
  If $A$ is a rectified formula then $\graphof A$ is a fograph.
\end{lemma}

\begin{proof}
  That  $\graphof A$ is a logical cograph follows immediately from the definition and Theorem~\ref{thm:cograph}. 
  \todo{}\lutz{maybe mention also fn 2-5 in arxiv-paper}
\end{proof}

\todo{def $\fequ$}

\begin{thm}
  Let $A,B$ be rectified formulas. Then
  $$
  A\fequ B \iff \graphof A =\graphof B
  $$
\end{thm}

\begin{proof}
  \todo{}
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Two atoms are \bfit{pre-dual} if their predicate symbols are dual
(e.g. $pxy$ and $\overline{p}yz$) and two literals are \bfit{pre-dual} if their
labels (atoms) are pre-dual. A \bfit{linked fograph} is a coloured fograph such
that every colour, called a \bfit{link}, consists of two pre-dual literals, and
every literal is either $\ttt$-labelled or in a link.

@@

\todo{define matching}

\todo{adjust notation}

@@

%%\subsection{First-order combinatorial proofs}

\begin{definition}
A \bfit{first-order combinatorial proof} of a fograph $G$ is a skew
bifibration $f: N \rightarrow G$ where $N$ is a fonet. A \bfit{first-order
combinatorial proof} of a formula $A$ is a combinatorial proof of its graph
$\graphof(A)$.
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{proposition}
\label{prop2}
Let $u$ and $v$ be two distinct vertices of a fograph $\graphof(A)$, then we have the equivalence
between:
\begin{itemize}
  \item $u$ and $v$ are adjacent in $\graphof(A)$
  \item $u$ and $v$ are connected by a switching path of $\FT(A)$, and if one of them is a universal quantifier, then the other is
	not a descendant of the former.
  \end{itemize}
\begin{proof}
By induction on $A$.
\begin{itemize}
  \item If $A$ is an atom, trivial.
  \item If $A = A_1 \cand A_2$, then we distinguish two cases:
    \begin{itemize}
      \item $u$ and $v$ are both in $A_1$ (resp. $A_2$): trivial by
	      the induction hypothesis.
      \item one of them is in $A_1$ and the other is in $A_2$: they are
	      adjacent in $\graphof(A)$ by definition. By Proposition \ref{prop1},
		    the one in $A_1$ (resp. $A_2$) is connected to the
		    vertex representing $A_1$ (resp. $A_2$) by a switching
		    path. Together with the two edges incident to $A_1 \cand
		    A_2$, we obtain a switching path connecting $u$ and $v$.
    \end{itemize}
  \item If $A = A_1 \cor A_2$, then we distinguish two cases:
    \begin{itemize}
      \item $u$ and $v$ are both in $A_1$ (resp. $A_2$): trivial by
	      the induction hypothesis.
      \item one of them is in $A_1$ and the other is in $A_2$: they are not
	      adjacent in $\graphof(A)$ by definition. It is clear that they
		    are not connected by a switching path.
    \end{itemize}
  \item If $A = \exists x \ A'$, then we distinguish two cases:
    \begin{itemize}
      \item $u$ and $v$ are both in $A'$: trivial by the induction
	      hypothesis.
      \item one of them is $\exists x$ and the other is in $A'$: trivial
	      by Proposition \ref{prop1}

    \end{itemize}
  \item If $A = \forall x \ A'$, then we distinguish two cases:
    \begin{itemize}
      \item $u$ and $v$ are both in $A'$: trivial by the induction
	      hypothesis.
      \item one of them is $\forall x$ and the other is in $A'$:
	      they are not adjacent in $\graphof(A)$ by definition and it is clear that
		    the former is a descendant of $\forall x$.
    \end{itemize}
\end{itemize}
\end{proof}
\end{proposition}

\begin{proposition}
If there exists an induced bimatching of the linked fograph $G = \graphof(A)$, then there exists a switching graph of the corresponding unification net which contains a cycle.
\begin{proof}
  Suppose that there exists a set $W$ inducing a bimatching in $G$.
  Then $(W, E_G)$ and $(W, L_G)$ are matchings.\\
  Let $E_W$ (resp. $L_W$) be the restriction of $E_G$ (resp. $L_G$) to $W$. \\
  If $E_W \cap L_W \neq \emptyset$, then there exist $u$ and $v$ such that $uv
  \in E_G$ and $uv \in L_G$. By Proposition \ref{prop2}, there exists a
  switching path of the formula tree of $A$. Together with the leap
  $uv$, this path induces a cycle in a switching graph of the
  corresponding unification structure. \\
  We can now suppose that $E_W$ and $L_W$ are disjoint. It is not difficult to
  see the existence of an alternating and elementary cycle in the bicoloured graph $(W, E_W \uplus L_W)$, i.e. a cycle of which the edges are alternately in $E_W$ and $L_W$ and containing no two equal vertices.
  By Proposition \ref{prop2}, this cycle induces a cycle in the unification
  structure. Now we want to construct a switching graph that contains this cycle.\\
  Consider a universal quantifier $\forall x$. If $\forall x \notin W$, then        
  we keep the incoming edge from its direct subformula and remove all the 
  dependencies. Otherwise, since $(W, L_G)$ is a matching, there exists a
  unique existential quantifier adjacent to $\forall x$ and we keep thus the
  corresponding edge in the unification structure. \\
  Now consider a $\cor$. We distinguish three cases:
  \begin{itemize}
    \item the cycle goes through none of the two branches (incoming edges) of
	    the $\cor$: we can choose an
	    arbitrary switching for this $\cor$
    \item the cycle goes through exactly one branch: we choose the corresponding
	    switching
    \item the cycle goes through both branches:
	    this means that there exist $v_L \in W$ (resp. $v_R$) in the left
		  (resp. right) branch, $u_L$, $u_R \in W$, such that
		  $u_Lv_L, u_Rv_R \in E_W$ and that the corresponding switching
		  path from $u_L$ to $v_L$ (resp. from $u_R$ to $v_R$) goes
		  through the left (resp. right) edge of $\cor$.

@@

\begin{proposition}
For any context $S$ and any formula $A$:
\begin{itemize}
  \item $\PE{A}$ is a formula containing no quantifier for any formula $A$.
  \item $\graphof(\PE{A}) = \graphof(A)$ by confounding the atoms $U_x$, $E_x$ with the variable
	  $x$. Thus, a map $f : \graphof(\PE{A}) \rightarrow \graphof(\PE{B})$ can be seen as a map
		$f : \graphof(A) \rightarrow \graphof(B)$.
  \item $\PE{(S\{A\})} = \PE{S}\{\PE{A}\}$.
\end{itemize}

@@

Now we prove that each map $g \in \{wk, ac, m, m_1, m_2 \}$ is a skew bifibration. To do that, it suffices to prove that $g$ is a fibration between the corresponding binding graphs since it is already a skew fibration on the corresponding fographs and it is label-preserving and existential-preserving.
\begin{center}
for each $x$-binder $b$ in $\graphof(\PE{B})$, for each vertex $v \in V(\graphof(\PE{A}))$
such that $g(v)$ is bound by $b$, there exists a unique binder $b'$ such
that $b'$ binds $v$.
\end{center}

@@

  Therefore, all of these maps are skew bifibrations and since skew bifibrations
on fographs compose (Lemma 10.32, \cite{hughes:fopws}), there exists a skew
bifibration from $\graphof(A)$ to $\graphof(B)$.

@@

\begin{proof}
By Theorem \ref{thm1}, there exists a formula $A'$ such that there is a proof
$\Pi$ of $A'$ in $\FOMLL$ and a derivation $D$ from $A'$ to $A$ consisting of
the $\wD$ and $\cD$ rules only. The proof $\Pi$ corresponds to a unique
unification net which is equivalent to the fonet corresponding to $\Pi$, i.e.,
the fograph $\graphof(A')$ together with the links of $\Pi$. By Lemma \ref{mlem}, 
there exists a skew bifibration $\graphof(A') \rightarrow \graphof(A)$. We have thus a
combinatorial proof of $A$.

@@

\begin{proof}
Consider the dervation $\Delta''$. If some $U_x$ (or $E_x$) is introduced
via weakening, then all the atoms it binds in $\PE{B}$ should also be introduced 
via weakening. In fact, an atom of $\PE{B}$ is introduced via weakening is 
equivalent to the fact that its corresponding vertex is not in the image of $f$. 
Since there is an edge from $U_x$ (resp. $E_x$) to all the literals it binds in the 
binding graph $\overrightarrow{\graphof(B)}$, if one of the atoms is in the image, 
$U_x$ (resp. $E_x$) should also be in the image since $f$ is a fibration on binding graphs.
